---
title: "Part2"
author: "Mohit Anand"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The aim of this report is to analyze the ToothGrowth DataSet in R.
As per the help file of this dataset, the response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).
First we will load the ggplot library and get the summary of ToothGrowth Dataset.
```{r}
library(ggplot2)

data("ToothGrowth")
str(ToothGrowth)
```
Since dose only has three values which are essentially categorical hence we convert it to factor.
```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

## Exploratory Analysis
Now we will create some plots to explore the data
```{r}
bxplt <- ggplot(aes(x=dose, y=len),data = ToothGrowth)+ geom_boxplot(aes(fill=dose)) + facet_grid(.~supp)+ xlab("Dose Amount") + ylab("Tooth Length")+ ggtitle(" Tooth Length compared to Dose amount")
print (bxplt)
```

We can also explore on the basis of Dose amount
```{r}
bxplt2 <- ggplot(aes(x=supp, y=len),data = ToothGrowth)+ geom_boxplot(aes(fill=supp)) + facet_grid(.~dose)+ xlab("Supplement") + ylab("Tooth Length")+ ggtitle(" Tooth Length compared to Delivery Method")
print (bxplt2)
```

## Hyposthesis Testing
Now we will perform Hypothesis testing to determine if the categorical variables affect the result i.e. the length of Tooth. 

### Supplement as a Factor
For this we will use t test. First we will run the test on the basis of supplement chosen.
```{r}
t.test(len~supp,data=ToothGrowth)
```
We can see that the p-value is more than 0.05 and the confidence interval has zero in it.
Therefore, we can conclude that supplement types don't have impact on the Tooth growth in this test.

### Dosage as a Factor
Now we shall run a t test to see if the Dosage is a Factor or not.
First we will split the Dosage data into subsets of two
```{r}
TG_dose1 <- subset (ToothGrowth, dose %in% c(0.5, 1.0)) 
TG_dose2 <- subset (ToothGrowth, dose %in% c(0.5, 2.0)) 
TG_dose3 <- subset (ToothGrowth, dose %in% c(1.0, 2.0)) 
```

Checking for dose levels (0.5,1.0)
```{r}
t.test(len~dose,data=TG_dose1)
```

Checking for dose levels (0.5,2.0)
```{r}
t.test(len~dose,data=TG_dose2)
```

Checking for dose levels (2.0,1.0)
```{r}
t.test(len~dose,data=TG_dose3)
```
As we can see for all the three t tests the p-value is much less than 0.05 and the confidence interval does not contain zero.
Based on this we can make a conclusion that tooth length is directly related to the dosage.
Hence we reject the null hypothesis.

### Assumptions
1. The sample is representative of the population of guinea pigs
2. For the t-tests, the variances are assumed to be different for the two groups being compared.
3. The distribution of sample means follows Central Limit Theorem

