---
title: "Stat Inference Part 1"
author: "Mohit Anand"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This is the part 1 submission of Statistical Inference Project. In this the distribution of averages of 40 exponentials with a thousand simulation is analyzed. The distribution obtained is compared with Central Limit Theorem. The following things are shown:
1. The Sample mean compare it to theoretical mean
2. The variance of sample and compare it to the theoretical varinace of the distribution
3. Distribution is approximately normal

###Simulation

```{r}
library(ggplot2)
set.seed(2456)
n<-40
lambda<-0.2
sim<-1000
sim_sample<-matrix(rexp(n*sim, rate = lambda),sim)
sim_mean<- apply(sim_sample,1,mean)
```

###Sample Mean Comparison
```{r}
samp_mean <- mean(sim_mean)
```

```{r}
theo_mean <- 1/lambda
```
Here we see that the two values of Sample mean and Theoretical mean are almost equal.

The theoretical mean is shown as Green line and the sample mean as Red.
```{r}
hist(sim_mean, xlab="mean of exponentials", ylab="frequency", main="Histogram of mean of 40 exponentials", col="blue")
abline(v = theo_mean, col="green")
abline(v = samp_mean, col="red")
```


### Variance Comparison

Sample's Variance and standard deviation
```{r}
#Standard deviation
sim_sd<- sd(samp_mean)

#Variance of Simulation
sim_var<-sim_sd^2
```

Theoretical Variance and Deviation
```{r}
#Theoretical deviation
theo_sd <- (1/lambda)/sqrt(n)

#Theoretical Variance
theo_var<- theo_sd^2
```
The Variance and standard deviation values are nearly equal

The plot approximatly  shows a normal distribution
```{r}
df <- data.frame(sim_mean)
plot_data <- ggplot(df,aes(x= sim_mean))
plot_data <- plot_data + geom_histogram(aes(y=..density..),fill ="green",color = "black") + 
  geom_density(colour="red") 
print(plot_data)
```


